### 2021-03-19 Chapter-1/Chapter-1.tex
Updates from Overleaf

Side channels are inevitable in modern computer systems as the sensitive
information may be leaked through many kinds of inadvertent behaviors, such as power, electromagnetic radiation, and even
sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
attacks result from vulnerable software and shared hardware components.
By observing program outputs or hardware behaviors, attackers can infer program
execution flows that manipulate secrets and guess secrets such as encryption
keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.

>>>>

Side-channels are ubiquitous in modern computer systems as sensitive information may be leaked through many kinds of negligent behaviors, such as power, electromagnetic radiation, or even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}. It is typically hard to fix all side-channel vulnerabilities for real-world software systems.

Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
attacks result from vulnerable software and shared hardware components.
By observing program outputs or hardware behaviors, attackers can infer program
execution flows that manipulate secrets and guess secrets such as encryption
keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
